Indoor Dining Shutdowns Negatively Affect Toronto Restaurants’ Performance and Business Practices

### 2021-02-27 outputs/paper/paper.Rmd
Fix a typo

Pearson’s Chi-squared (*X*^2^) tests were conducted to see if there is a statistically significant difference between responses regarding restaurant adjustments in the intervention and control conditions. The test results show that the p-value of each of those adjustments is less than 0.001, meaning there is a significant relationship between condition (whether or not indoor dining services were shut down or not) and adjustments made to menu prices, hours of operation, and days of operations. That is, restaurants in the intervention condition were more likely to change their menu prices and reduce their operational hours and days.

>>>>

Pearson’s Chi-squared (*X*^2^) tests were conducted to see if there is a statistically significant difference between responses regarding restaurant adjustments in the intervention and control conditions. The test results show that the p-value of each of those adjustments is less than .001, meaning there is a significant relationship between condition (whether or not indoor dining services were shut down or not) and adjustments made to menu prices, hours of operation, and days of operations. That is, restaurants in the intervention condition were more likely to change their menu prices and reduce their operational hours and days.
